\myTitle

### 2024-05-13 data-accessibility.tex
Clean up to make it a GitHub repo
Eric final edits

{\sc microhaplot} is available as an R package with these associated links:
\begin{itemize}
\item Stable version available on CRAN (when available): \url{https://CRAN.R-project.org/package=gscramble}
\item Development version and entire revision history on GitHub: \url{https://github.com/eriqande/gscramble}
\item Online version of all package documentation: \url{https://eriqande.github.io/gscramble}
\item Data repository with full data from pig, Chinook, and bird (maybe?) data sets \url{https://dryad.something.or.other}
\end{itemize}
\mbox{}

>>>>

\begin{itemize}
\item Stable version of \gscramble{} available on CRAN: \url{https://CRAN.R-project.org/package=gscramble}
\item Development version and entire revision history on GitHub: \url{https://github.com/eriqande/gscramble}
\item Online version of all package documentation: \url{https://eriqande.github.io/gscramble}
\item Data and code repository with simulation analyses and steelhead-cutthroat analyses: \url{https://github.com/eriqande/gscramble-paper-sims-and-analyses} (To be transferred to Dryad or Zenodo upon acceptance).
\item Data and code repository for pig analyses: {NEED THE URL FOR THIS} (To be transferred to Dryad or Zenodo upon acceptance)
\end{itemize}
\mbox{}
